Open integrated distance sampling for modelling age-structured population dynamics

### 2024-07-23 Manuscript_Nilsen_Nater.qmd
Edit to figure 1 caption

![Graphical representation of the annual ptarmigan life cycle with two age classes and the data sources included in the integrated distance sampling model. Juvenile~t~ = juveniles in year $t$. Adult~t~ = adults in year $t$. $R_t$ = recruitment rate in year $t$. $S_t$ = survival probability from year $t$ to $t+1$.](Figures/RypeIDSM_structure.png){#fig-model}

>>>>

![Graphical representation of the annual ptarmigan life cycle with two age classes under a post-breeding census and the data sources included in the integrated distance sampling model. Solid arrows represent relationships within the ptarmigan life cycle; dotted arrows visualize information flow from data sources to parameters. Blue and pink data nodes originate from distance sampling and line transect surveys, respectively. Juvenile~t~ = juveniles in year $t$. Adult~t~ = adults in year $t$. $R_t$ = recruitment rate in year $t$. $S_t$ = survival probability from year $t$ to $t+1$.](Figures/RypeIDSM_structure.png){#fig-model}
